---
title: "March Order"
author: "CofI-Shiny"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
output: pdf_document
params:
  full: full.xlsx
  rsvp: rsvp.xlsx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(readxl)
library(knitr)
library(kableExtra)

```

```{r}
FullDF <- read_excel(params$full, col_names =TRUE, skip=1) %>% select(LN=`Last Name`, FN=`First Name`,Yrs=`Decimal Years Since Hire Date`) 

RSVP <- read_excel(params$rsvp, col_names = TRUE) %>% select(Name, Response=`Will you be part of the procession for the 2018 Convocation?`) %>% filter(Response == "Yes") %>% separate(col=Name, into = c("FN", "LN"), sep = "[:space:]", extra = 'merge')

retDF <- inner_join(FullDF, RSVP, by=c("LN","FN")) %>% 
  arrange(desc(Yrs), LN) 
notComing <- anti_join(FullDF, RSVP, by=c("LN","FN")) %>% 
  arrange(desc(Yrs), LN)

numRSVP <- length(retDF$LN)

retDF$position <- 1:numRSVP
notComing$position <- (numRSVP+1):(numRSVP+length(notComing$LN))

```

The following tables provide the march order for faculty and staff. **In the event that someone is not present, the person on the left has priority to move up.**

## Attendees
The following have confirmed their attendence.

```{r attend}
lseq <- seq(from=1, to=numRSVP, by=2)

left <- retDF %>% filter(position %in% lseq) %>% 
  mutate(Left_Name = paste(LN,FN, sep=", ")) %>%
  select(Left_Name)

right <- retDF %>% filter(!(position %in% lseq)) %>%
  mutate(Right_Name = paste(LN,FN, sep=", ")) %>%
  select(Right_Name)

if(numRSVP%%2==1){
  right <- rbind.data.frame(right, data.frame(Right_Name=" "))
}

cbind.data.frame(lseq,left,right) %>% kable("latex", booktabs=TRUE) %>% 
  kable_styling(latex_options = c("stiped", "scale_down"))
```

## Additional Possible Attendees
The following have not confirmed attendence, if any do attend they will march in the following order **after** the above list of attendees.

```{r notAttend}
lenNC <- (numRSVP+length(notComing$LN))
lseq2 <- seq(from=ifelse(numRSVP%%2==1, numRSVP, numRSVP+1), to=lenNC, by=2)

left2 <- notComing %>% filter(position %in% lseq2) %>% 
  mutate(Left_Name = paste(LN,FN, sep=", ")) %>%
  select(Left_Name)

right2 <- notComing %>% filter(!(position %in% lseq2)) %>%
  mutate(Right_Name = paste(LN,FN, sep=", ")) %>%
  select(Right_Name)

if(lenNC%%2==1){
  right2 <- rbind.data.frame(right2, data.frame(Right_Name=" "))
}

cbind.data.frame(lseq2,left2,right2) %>% kable("latex", booktabs=TRUE) %>% 
  kable_styling(latex_options = c("stiped", "scale_down"))
```